---
title: "R Notebook"
output: html_notebook
---
# compare Berlin Hot Spots
This is about the month in which accidents happen.
We should look into The distribution of accidents over the month of the year (maybe for Berlin, not for all of Germany)

Barcharts are OK, because they are simple.

I should have the line for Berlin in the barchart for the hot spots, not the single hot spot but the barchart summed over all hot spots.

I have tried to calculate a medium month for each hot spot, and to put it in the barcharts for the individual hot spot. But my linear transformation is not working correctly.

```{r}
#install the osmdata, sf, tidyverse and ggmap package
if(!require("osmdata")) install.packages("osmdata")
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("sf")) install.packages("sf")
library(tidyverse)
library(osmdata)
library(sf)
```

```{r}
# laptop
rm(list=ls())
setwd("~/Documents/ds/sem3/Felix/transport/mycode/data-visualisation/streets")
acci <- read.csv('../../data/Unfallorte2019_LinRef_with_AGS.csv', sep=';')
hot_spots <- read.csv('../../data/berlin-hotspots.csv', sep=',')
```

```{r}
streets <- readRDS('../../data/overpass-berlin-streets.Rds')
small_streets <- readRDS('../../data/overpass-berlin-small-streets.Rds')
```

```{r}
dfMo <- data.frame()
dfMonth <- data.frame()
```

```{r}
accib <- acci %>% dplyr::filter(ULAND==11) %>% 
  select('UMONAT') %>%
  table()
x <- barplot(accib/accib[6])
#p <- plot(accib, type='l', col='blue')
#print(p)
lines(x=x, y=accib/accib[6],type='l',col='blue')
```

```{r}
res = 0.001
for (i in 1:5) {
  print(i)
# data from csv
  lat <- hot_spots$lat[i]
  #print(lat)
  lon <- hot_spots$long[i]
  #print(lon)
xleft = lat -res
xright = lat + res
ybottom = lon - res
ytop = lon + res
xlim=c(xleft,xright)
ylim=c(ybottom,ytop)
# accidents in hotspot window
acci_hot_spots<- list()
a1 <- acci %>% filter(XGCSWGS84 > xleft) %>% 
  filter(XGCSWGS84 < xright) %>% 
  filter(YGCSWGS84 > ybottom) %>% 
  filter(YGCSWGS84 < ytop)
# write as csv
write.csv(a1,paste('hotspot',i,'.csv',sep=''))
poa <- a1 %>% select(XGCSWGS84 , YGCSWGS84) %>% 
  rename( X= XGCSWGS84 , Y= YGCSWGS84)
acci_hot_spots[i] <- a1
# create image / plot
p<- ggplot() +
  geom_sf(data = streets$osm_lines,
          inherit.aes = FALSE,
          color = "black",
          size = .4,
          alpha = .8)  +
  geom_sf(data = small_streets$osm_lines,
          inherit.aes = FALSE,
          #color = "#ffbe7f",
          color='orange',
          size = .2,
          alpha = .6) +
  geom_point(data = poa, 
             aes(x=X, y=Y), 
             color='red', 
             size=.2, 
             alpha=.7)+
  coord_sf(xlim = xlim, 
           ylim = ylim,
           expand = FALSE)
# save image / plot
png(paste('hotspot',i,'.png',sep=''))
print(p)
dev.off()
}

```
Do statistics for the hotspots
```{r}
mid_month <- list() 
# boxplot(dfMonth[2:6]) # this is not what I want.
for (i in 2:6){
  a <- 0
  for (j in 1:12) {
    a <- a + dfMonth[j,i]*j
    #print(a)
  }
  #print(i)
  print(a/sum(dfMonth[,paste(i-1)]))
  mid_month[i-1] <- a/sum(dfMonth[,paste(i-1)])
}
 a <- 0
  for (j in 1:12) {
    a <- a + dfMonth[j,'summed']*j
  }
 print(a/sum(dfMonth[,'summed']))
 mid_month[6]<- a/sum(dfMonth[,'summed'])
```

````{r}
dfMonth <- data.frame(x=rep(0,times=12))
for (i in 1:5){
#print(i)
a1 <- read.csv(paste('hotspot',i,'.csv',sep=''))
dfm <- data.frame(a=rep(0,times=12))
n<-nrow(a1)
for (j in 0:n){
  #print(j)
  dfm[a1[j,'UMONAT'],'a'] <-   dfm[a1[j,'UMONAT'],'a']+1 }
dfMonth[paste(i)] <- dfm[,'a']
}
```

```{r fig.height=3, fig.width=4}
lin_trans <- function (x,a,b){return(x*(b-a))}

for (i in 2:6) {
#  print(dfMo[,i])
  posi <- barplot(dfMonth[,i], ylim=c(0,5.3), main='accidents per month at Berlin hot spot')
  #print(mid_month)
  #print(posi[1]==0.7)
  v <- 1.2*(mid_month[[i]]-1)
  print(c(mid_month[[i]],v))
    #(mid_month[[i-1]])*(posi[2,'V1']-posi[1,'V1'])
  abline(v=v, lty='dashed')
  abline(v=(posi[6]+posi[7])/2)
  #abline(v=posi[6])
}
# this is not correct yet.
```
The mean value for the month shoul be transformed, because the middle is not at 6 but at posi[6]+posi[7])/2. More simple: 1->posi[1]=0.7 and 12->posi[12]=13.9

So the mid_month has to be transformed to suit this.

1 -> posi[1]
2 -> posi[2]
x ->  x * (posi[2]-posi[1]/(2-1) 


```{r}
for( i in 1:12){
  #print(i)
# print(sum(dfMo[paste(i),]))
dfMonth[i,'summed'] <- as.numeric(sum(dfMonth[i,2:6]))
}

#dfMo[1,'summed']='bla'
```

```{r}
#print(dfMo)
barplot(dfMonth[,'summed'], ylim=c(0,12), main='Accidents per month summed over 5 hotspots')
```
Fazit: Month irrelevant for number of accidents at these 5 hot spots


```{r fig.height=6, fig.width=10}
#png(filename="plot1.png", width=200, height=300, bg="white")
png(filename='small-multiple-hotspots-UMONAT.png', width=600 , height=300)
par(mfrow=c(2,3))
par(mar=c(0.5, 4.5, 2.5, 0.5))
x<-barplot(dfMonth[,'summed'], ylim=c(0,12), main='summed accidents')
lines(x=x, y=accib/accib[6]*11,type='l',col='blue')
legend('bottomleft',
       legend='Berlin, total, scaled', 
       col='blue', 
       pch='---',
       bty='y',
       text.col='blue')

for (i in 2:6) {
  par(mar=c(0.5, 4.5, 2.5, 0.5))
  barplot(dfMonth[,i], ylim=c(0,12) , main = paste('hotspot',i-1))
  }
dev.off()

```


How could I represent this graphically? Just a vertical line at the computed value at the x-axis?
